\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
%\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{enumerate}
\usepackage{indentfirst}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{amssymb,amsmath}
\usepackage{fancyhdr}
\usepackage{tabu}
\usepackage{paracol}
\usepackage{multicol}
\usepackage{graphics}
\usepackage{textcomp}
\usepackage{fontawesome}



\setlength{\parindent}{0cm}
\setlength{\parskip}{2mm}
\renewcommand{\baselinestretch}{1.25}


\newcommand{\MyName}{Chenyi ``Lisa'' Zhu}
\newcommand{\MySchool}{JHU $'$22}
\newcommand{\MyContact}{czhu26@jhu.edu}

\newcommand{\DocTitle}{APS/IBM Internship for Undergraduate Women - Letter}
\fancypagestyle{plain}{
  \fancyhead{}
  \fancyfoot[L]{\MyName{}}
  \fancyfoot[R]{\MySchool{}}
  \fancyfoot[R]{\MyContact{}}
  \renewcommand{\headrulewidth}{0pt}
}

\fancypagestyle{firstpage}{
  \fancyhead{}
  \fancyhead[L]{
    1/15/2020 \\~\\ \break \large{\textbf{\DocTitle}}
  }
  \fancyhead[R]{
      {\MyName{}} \\ \MySchool \\ \MyContact
  }

  \renewcommand{\headrulewidth}{0.2pt}
  \setlength{\headheight}{50pt}
  \setlength{\headsep}{12pt}
}

\geometry{
%a4paper,
left = 0.5in,
right = 0.5in,
top = 0.5in,
bottom = 0.5in,
}

\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    filecolor=magenta,      
    urlcolor=blue,
}

\begin{document}

%\begin{center}
\iffalse
\columnratio{0.30, 0.40, 0.30}

\begin{paracol}{3}
	%\begin{center}
	\textcolor{white}{ }\\
	{\Huge \textbf{Lisa Zhu}}
	%\end{center}
	
	\switchcolumn
	\begin{center}
	\begin{tabular}{l l}
		\textbf{Github:} & \href{https://github.com/chenyi00}{github.com/chenyi00}\\~\\
		\textbf{LinkedIn:} & \href{https://www.linkedin.com/in/chenyi-jhu/}{linkedin.com/in/chenyi-jhu}\\
		%\textbf{Portfolio:} &\href{https://ugrad.cs.jhu.edu/~czhu26/}{ugrad.cs.jhu.edu/$\sim$czhu26}\\
	\end{tabular}
	\end{center}
	\switchcolumn
	%\iffalse
	\begin{center}
	\begin{tabular}{l l}
		\textbf{Phone:} & (443) 604-3051\\~\\
		\textbf{Email:} & czhu26@jhu.edu\\
	\end{tabular}
	\end{center}
	%\fi
	%\raggedleft
	%\textbf{Phone:} (443) 604-3051\\%~\\
	%\textbf{Email:} czhu26@jh.edu\\
\end{paracol}
\fi
%\vspace{-2mm}

\begin{center}
	{\Huge \textbf{Chenyi Zhu}}\\
	\vspace{2mm}
	{
	\small Johns Hopkins University, Baltimore, MD\\
	\footnotesize
	\faEnvelopeSquare \, \href{mailto:czhu26@jhu.edu}{czhu26@jhu.edu} $\bullet$ \faHome \, \href{https://chenyi00.github.io/}{chenyi00.github.io} $\bullet$ \faLinkedinSquare \, \href{https://www.linkedin.com/in/chenyi-jhu/}{chenyi-jhu} $\bullet$ \faGithub \, \href{https://github.com/chenyi00}{chenyi00}}
\end{center}
\vspace{-2mm}

%Education section
{\large \textbf{\textsc{Education}}}
\vspace{5pt}
\hrule
\columnratio{0.75}
\begin{paracol}{2}
	\textbf{The Johns Hopkins University}\\
	\textit{Majors: Computer Science, Applied Math \& Statistics}\\
	\textit{GPA: 3.50/4.00}\\
	\textit{Honor: Dean's List}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{2018$\sim$2022}\\~\\~\\
	%\raggedleft\textit{2018$\sim$2020}\\~\\
\end{paracol}
\vspace{3mm}

%Activities & leadership
{\large \textbf{\textsc{Work \& Internships}}}
\vspace{5pt}
\hrule

% MT
\begin{paracol}{2}
	\textbf{Research: Neural Machine Translation}\\
	\textit{Student Researcher}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Present}
\end{paracol}\vspace{-1mm}
\textit{Advisor: Dr. Philipp Koehn $\cdot$ Center for Language and Speech Processing (\textbf{CLSP})}
\vspace{-2mm}
\begin{itemize}
	\item Exploring ways to integrate glossaries and inline instructions into machine translation models at runtime to enforce specialized terminology to prevent degradation of model performance. 
	 
\end{itemize}
\vspace{-2mm} 

% IACL
\begin{paracol}{2}
	\textbf{Internship: Medical Image Segmentation}\\
	\textit{Delineator}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Present}
\end{paracol}\vspace{-1mm}
\textit{Advisor: Shangxian Wang $\cdot$ Image Analysis \& Communications Lab (\textbf{IACL})}
\vspace{-2mm}
\begin{itemize}
	\item Working on segmentation of the thalamus based on MRI scans.\vspace{-3mm}
	\item Creating training data for medical image segmentation algorithm.
\end{itemize}
\vspace{-2mm} 

%Teaching assistant
\begin{paracol}{2}
	\textbf{Teaching: C/C++}\\
	\textit{Course Assistant}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Present}
\end{paracol}\vspace{-1mm}
%\textit{Advisors: Dr.Robert Leheny, Dr.Brice Ménard: Bloomberg Center for Physics and
 %Astronomy (\textbf{JHU})}
\vspace{-2mm}
\begin{itemize}
	\item TA for Intermediate Programming, a core computer science course. 
	\vspace{-3mm}
	\item Assisting students in class with coding practices, held office hours, and graded assignments.
\end{itemize}
\vspace{-2mm}

%Teaching assistant
\begin{paracol}{2}
	\textbf{Teaching: \href{https://github.com/chenyi00/physics-2}{Electromagnetism}}\\
	\textit{Learning Assistant}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Jan 2020 $\sim$ May 20}
\end{paracol}\vspace{-1mm}
%\textit{Advisors: Dr.Robert Leheny, Dr.Brice Ménard: Bloomberg Center for Physics and
 %Astronomy (\textbf{JHU})}
\vspace{-2mm}
\begin{itemize}
	\item TA for Physics II, a core engineering course. \vspace{-3mm}
	\item Attended lectures twice a week, taught Friday sections to help students review class materials and solve additional problems, and held office hours weekly.
	\vspace{-3mm}
	\item Compiled supplementary notes on the mathematics of electromagnetism for students to help understand the material.
\end{itemize}
\vspace{-2mm}


%Research Internship
\columnratio{0.7, 0.3}
\begin{paracol}{2}
	\textbf{Internship: Electro-analgesic Pain Modulation}\\
	\textit{Student Researcher}
	\switchcolumn \hfill
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Mar 2019 $\sim$ Present}
\end{paracol}\vspace{-1mm}
\textit{Advisors: Dr. Yun Guan, Dr. Amir Manbachi, Dr. Allan Belzberg et al. $\cdot$ Neurosurgery
Pain Institute (\textbf{JHMI})}
\vspace{-3mm}
\begin{itemize}
	\item Reverse-engineered ``Scrambler'' electro-analgesic device for chronic pain relief with 
	Arduino and various other electronic components, and reconstructed electrical waveforms 
	with C/C++.
	\vspace{-3mm}
	\item Visualized individual waveforms with the Spike2 data acquisition system in combination 
	with MATLAB and categorized each waveform based on its distinct stimulation patterns.
	\vspace{-3mm}
	\item Conducted testing trials and used ImageJ cellular analysis software to examine stimulation effects on DRG neurons.
\end{itemize}
\vspace{-2mm} 

\pagebreak

%Design team
\begin{paracol}{2}
	\textbf{Design Team: \href{https://nearspace.jhu.edu/}{Weather Balloon Project}}\\
	\textit{Project Lead}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Mar 2019 $\sim$ Present}
\end{paracol}\vspace{-1mm}
\textit{Advisor: Dr. Brice Ménard $\cdot$ Bloomberg Center for Physics and Astronomy (\textbf{JHU})}
\vspace{-2mm}
\begin{itemize}
	\item  Launched payloads with helium weather balloons to high altitudes of 84,000
	feet; collected atmospheric data along the payload's ascent to and descent from the 
	stratosphere.\vspace{-3mm}
	\item Created effective payload designs containing electronic sensors and devices including
	cameras, multiple sensors, and APRS \& GSM tracking modules, programmed with C, Python, 
	Arduino, and Shell scripts to establish communication between ground and payload,
	driven by Raspberry Pi computers.\vspace{-3mm}
	\item Organized and prepared the team for meetings, day-of-launch planning,
	and post-launch data analysis workshops.
\end{itemize}
\vspace{-2mm}

%Design team
\begin{paracol}{2}
	\textbf{Design Team: EpiX}\\
	\textit{Engineering Lead}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Nov 2018 $\sim$ Present}
\end{paracol}\vspace{-1mm}
\textit{Advisors: Dr. Youseph Yazdi $\cdot$ Center for Bioengineering Innovation and
Design (\textbf{CBID}); Martin Jacobsen $\cdot$ Becton Dickson (\textbf{BD})}
\vspace{-2mm}
\begin{itemize}
	\item Performed product research and designed novel extendable Tuohy needle 
	prototypes aimed to reduce patient and 
	physician discomfort in current epidural procedures and to save \$162 million/year for 
	hospitals.\vspace{-3mm}
	\item Prototyped with Fusion360 and performed finite
	element analysis (FEA) to test model's efficacy and usability.\vspace{-3mm}
	\item Collaborated with the School of Medicine and BD to optimize our
	model for clinical and industrial settings.\vspace{-3mm}
	\item Applied and received Malinow Grant (\$4,000) to fund the project over 
	the summer of 2019 seeking IRB approval.\vspace{-3mm}
	\item Selected to present at ASA 2020. 
\end{itemize}
%\vspace{-2mm} 

% Volunteer & leadership
{\large \textbf{\textsc{Volunteer \& Leadership}}}
\vspace{5pt}
\hrule

% Honduras
\begin{paracol}{2}
	\textbf{Global Medical Brigades}\\
	\textit{Executive Board Member $\cdot$ Volunteer}
	\switchcolumn
	\raggedleft\textbf{Tegucigalpa, Honduras}\\
	\raggedleft\textit{Jan 19 $\sim$ May 20}
\end{paracol}\vspace{-1mm}
\vspace{-2mm}
\begin{itemize}
	\item Assisted three local Honduran communities to build infrastructure in healthcare, sanitation, and clean water systems.\vspace{-3mm}
	\item Organized donation drive for over 1400 sanitation bundles and contacted companies to sponsor future brigades.
\end{itemize}
\vspace{-2mm}

%Small group
\begin{paracol}{2}
	\textbf{First-year Small Group}\\
	\textit{Junior Mentor}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 20 $\sim$ Present}
\end{paracol}\vspace{-1mm}
\vspace{-2mm}
\begin{itemize}
	\item Help incoming freshmen navigate an online college experience.
	\vspace{-3mm}
	\item Organize discussions regarding current issues/advances in computer science.
\end{itemize}

% Personal Projects
{\large \textbf{\textsc{Personal Projects}}}
\vspace{5pt}
\hrule

% UAV
\begin{paracol}{2}
	\textbf{\href{https://ugrad.cs.jhu.edu/~czhu26/new_sub/projects/drone.html}{Project Ada}}\\
	\textit{Engineer}
	\switchcolumn
	\raggedleft\textbf{Birmingham, AL}\\
	\raggedleft\textit{May 2020 $\sim$ Aug 2020}
\end{paracol}\vspace{-1mm}
\vspace{-2mm}
\begin{itemize}
	\item Built and deployed a quadcopter drone from scratch.
\end{itemize}
\vspace{-2mm}

% Observatory
\begin{paracol}{2}
	\textbf{\href{https://ugrad.cs.jhu.edu/~czhu26/new_sub/projects/observatory.html}{Night Sky}}\\
	\textit{Telescope Operator}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{June 2019 $\sim$ Present}
\end{paracol}\vspace{-1mm}
\vspace{-2mm}
\begin{itemize}
	\item Certified operator of the Morris W. Offit telescope at JHU.
	\vspace{-3mm}
	\item Photographed planets in the solar system and stars beyond.
	%\vspace{-3mm}
\end{itemize}

\pagebreak
%Skills and interests
{\large \textbf{\textsc{Skills \& Interests}}}
\vspace{5pt}
\hrule
\columnratio{0.12}
\begin{paracol}{2}
\raggedleft
\textbf{Technical:}\\
\textbf{Courses:}\\~\\~\\
%\textbf{Hobbies:}\\
\textbf{Certificates:}\\~\\
\textbf{Languages:}\\
\textbf{Interests:}\\
%\textbf{Honors:}
\switchcolumn
\raggedright
Git, Java, C/C++, Python, MATLAB, \LaTeX, HTML/CSS/JS, R, AWS, CAD, Arduino, Raspberry Pi.\\
%, AWS, Microsoft Azure, Office, Linux, PHP\\
Algorithms, Object-Oriented Programming, Human Language Technology, AI, Data Structures, Intermediate Programming, Optimization I, Probability \& Statistics, Linear Algebra \& Differential Equations, Linear Signals \& Systems, Discrete Math, Calculus III, Electromagnetism, Mechanics.\\
%Circuit Design, Microsoft Office, 
%Photography, piano, reading, travelling.\\
Bloomberg Certificate (Bloomberg L.P., 6/2020), Radio Operator (ARRL, 6/2019), Telescope Operator (Maryland Space Grant Consortium, 6/2019).\\
English (fluent), Mandarin (fluent), French (intermediate), Latin (elementary).\\
Software Engineering, Machine Translation, Computational Research, Aviation \& Avionics.\\
%Dean's List.
\end{paracol}
%\thispagestyle{empty}
\end{document}
	
