\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{enumerate}
\usepackage{indentfirst}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{amssymb,amsmath}
\usepackage{fancyhdr}
\usepackage{tabu}
\usepackage{paracol}
\usepackage{multicol}
\usepackage{graphics}
\usepackage{textcomp}
\usepackage{fontawesome}

\setlength{\parindent}{0cm}
\setlength{\parskip}{2mm}
\renewcommand{\baselinestretch}{1}


\newcommand{\MyName}{Lisa Zhu}
\newcommand{\MySchool}{JHU $'$22}
\newcommand{\MyContact}{czhu26@jhu.edu}

\newcommand{\DocTitle}{APS/IBM Internship for Undergraduate Women - Letter}
\fancypagestyle{plain}{
  \fancyhead{}
  \fancyfoot[L]{\MyName{}}
  \fancyfoot[R]{\MySchool{}}
  \fancyfoot[R]{\MyContact{}}
  \renewcommand{\headrulewidth}{0pt}
}

\fancypagestyle{firstpage}{
  \fancyhead{}
  \fancyhead[L]{
    1/15/2020 \\~\\ \break \large{\textbf{\DocTitle}}
  }
  \fancyhead[R]{
      {\MyName{}} \\ \MySchool \\ \MyContact
  }

  \renewcommand{\headrulewidth}{0.2pt}
  \setlength{\headheight}{50pt}
  \setlength{\headsep}{12pt}
}

\geometry{
%a4paper,
left = 0.4in,
right = 0.4in,
top = 0.4in,
bottom = 0.4in,
}
\iffalse
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    filecolor=magenta,      
    urlcolor=blue,
}
\fi

\begin{document}

\pagenumbering{gobble}

\begin{center}
	{\huge \textbf{Chenyi ``Lisa'' Zhu}}\\
	\vspace{2mm}
	{
	%\small 1 E. University Pkwy, Baltimore, MD 21218\\
	\footnotesize
	\faMobile \, (443) 604-3051 | \faEnvelopeSquare \, \href{mailto:cyzhu2000@gmail.com}{\underline{cyzhu2000@gmail.com}} | \faHome \, \href{https://chenyi00.github.io/}{\underline{chenyi00.github.io}} | \faLinkedinSquare \, \href{https://www.linkedin.com/in/chenyi-jhu/}{\underline{chenyi-jhu}} | \faGithub \, \href{https://github.com/chenyi00}{\underline{chenyi00}}}
\end{center}
\vspace{-5mm}

%Education section
{\large \textbf{\textsc{Education}}}
\vspace{5pt}
\hrule
\columnratio{0.83}
\begin{paracol}{2}
	\textbf{Johns Hopkins University}\\
	\textbf{Majors:} \textit{B.S. Computer Science, Applied Math (GPA 3.52)}\\
	\textbf{Honors:} \textit{Dean's List, Malinow Grant (\$4,000)}\\
	\textbf{Courses:} \textit{Algorithms, Object-Oriented Programming, Data Mining, Optimization, Machine Learning, Computer Systems, Probability, Statistics, Linear Algebra \& Differential Equations, Calculus}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Expected May 2022}
\end{paracol}

%Skills and interests
{\large \textbf{\textsc{Skills}}}
\vspace{5pt}
\hrule
\columnratio{0.135}
\begin{paracol}{2}
\raggedleft
\textbf{Programming:}\\
\textbf{Software:}\\
%\textbf{Projects:}\\
\textbf{Certificates:}\\
\textbf{Languages:}\\

\switchcolumn
\raggedright
Java, C/C++, Python, HTML/CSS, JavaScript (Ember), MATLAB, R, Assembly x86, SQL (Postgre).\\
Git, PyTorch, AWS, \LaTeX, CAD, Bloomberg Terminal, Microsoft Office. \\

%\href{https://ugrad.cs.jhu.edu/~czhu26/new_sub/projects/drone.html}{Ada the Quadcopter}, \href{https://ugrad.cs.jhu.edu/~czhu26/new_sub/projects/observatory.html}{Night Sky} \\
%HTML/CSS/JS, AWS, Microsoft Azure, Office, Linux, PHP, CAD, \LaTeX, Arduino, Raspberry Pi, CAD.\\

BMC Certificate (Bloomberg LP, 6/2020), Telescope Operator (Space Grant Consortium, 6/2019).\\
%, Radio Operator (ARRL, 6/2019), Telescope Operator (Maryland Space Grant Consortium, 6/2019).\\
Mandarin, English, French.\\
\end{paracol}
\vspace{2mm}

%Activities & leadership 
{\large \textbf{\textsc{Internships \& Projects}}}
\vspace{5pt}
\hrule
\columnratio{0.83}
% LinkedIn
\begin{paracol}{2}
	\textbf{Internship: Site Reliability Engineer @ LinkedIn}\\
	\textit{Undergraduate Intern $\cdot$ LinkedIn Marketing Solutions}
	\switchcolumn
	\raggedleft\textbf{Sunnyvale, CA}\\
	\raggedleft\textit{June 2021$\sim$ Present}
\end{paracol}\vspace{-5mm}
\begin{itemize}
	\item Built real-time feedback mechanisms into internal availability diagnostics tool to collect actionable developer feedback and to effectively analyze user sentiment, enabling the team to improve the existing application and to add/adjust features accordingly. \vspace{-3mm}
	\item Performed on-call duties to manage and debug system outages or performance issues.
\end{itemize}
\vspace{-3mm} 

% MT
\begin{paracol}{2}
	\textbf{Research: Neural Machine Translation}\\
	\textit{Student Researcher $\cdot$ Center for Language and Speech Processing}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Present}
\end{paracol}%\vspace{-2mm}
%\textit{Advisor: Dr. Philipp Koehn}
\vspace{-5mm}
\begin{itemize}
	%\item Exploring ways to integrate glossaries and inline instructions into machine translation models at runtime to enforce specialized terminology to prevent degradation of model performance. 
	 \item Synthesized parallel corpora to include previously unseen single-word terminologies to distribute relevant information on the global pandemic through the TICO-19 dataset for low-resource languages.\vspace{-3mm}
	 \item Working to incorporate multi-word terms by generating efficient, order-sensitive embeddings with Python.
\end{itemize}
\vspace{-3mm} 

% OOSE
\columnratio{0.6}
\begin{paracol}{2}
	\textbf{Design Team: GOOSE}\\
	\textit{Software Engineer $\cdot$ Department of Computer Science }
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Dec 2020}
\end{paracol}\vspace{-5mm}
\begin{itemize}
	\item Created \href{https://goosegang-foodtruck.herokuapp.com/}{\textbf{\underline{MyCooksApp}}}, a social network application to support local small businesses by connecting food trucks and potential customers; built mainly in Java following CI/CD and AGILE development principles.\vspace{-3mm}
	\item Integrated Google Maps JavaScript API, thus allowing food trucks to see and update locations, and customers to rank food trucks with regard to relative distances in real time.
\end{itemize}
\vspace{-3mm} 

% IACL
\begin{paracol}{2}
	\textbf{Internship: Medical Image Segmentation}\\
	\textit{Delineator $\cdot$ Image Analysis \& Communications Lab}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Present}
\end{paracol}
%\textit{Advisor: Shangxian Wang $\cdot$ 
\vspace{-5mm}
\begin{itemize}
	\item Traced thalamus segmentation based on MRI scans and created training data for image segmentation algorithm.
\end{itemize}
\vspace{-3mm} 

%Research Internship
\columnratio{0.7, 0.3}
\begin{paracol}{2}
	\textbf{Internship: Electro-analgesic Pain Modulation}\\
	\textit{Student Researcher $\cdot$ Neurosurgery Pain Institute}
	\switchcolumn \hfill
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Mar 2019 $\sim$ Present}
\end{paracol}\vspace{-1mm}
%\textit{Advisors: Dr. Yun Guan, Dr. Amir Manbachi, Dr. Allan Belzberg et al. $\cdot$ Neurosurgery
%Pain Institute (\textbf{JHMI})}
\vspace{-3mm}
\begin{itemize}
	\item Reverse-engineered ``Scrambler'' electro-analgesic device for chronic pain relief with Arduino and various other electronic components, and reconstructed electrical waveforms with C/C++.\vspace{-3mm}
	\item Visualized individual waveforms with the Spike2 data acquisition system in combination with MATLAB and categorized each waveform based on its distinct stimulation patterns.\vspace{-3mm}
	\item Conducted testing trials and used ImageJ cellular analysis software to examine stimulation effects on DRG neurons.
\end{itemize}
\vspace{-3mm} 

% Balloon
\begin{paracol}{2}
	\textbf{Design Team: \href{https://nearspace.jhu.edu/}{\underline{Weather Balloon Project}}}\\
	\textit{Project Lead $\cdot$ Bloomberg Center for Physics and Astronomy}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Mar 2019 $\sim$ Present}
\end{paracol}\vspace{-5mm}
%\textit{Advisor: Dr. Brice Ménard $\cdot$ Bloomberg Center for Physics and Astronomy (\textbf{JHU})}
\begin{itemize}
	\item  Launched payloads with helium weather balloons to high altitudes of 84,000 feet; collected atmospheric data along the payload's ascent to and descent from the stratosphere.\vspace{-3mm}
		\item Designed robust reusable payload, modeled various components such as camera mounts using AutoCAD Fusion.\vspace{-3mm}
	\item Prepared electronic devices including cameras, atmospheric sensors, and APRS \& GSM tracking modules, programmed with C, Python, and bash scripts, driven by Raspberry Pi.
\end{itemize}
\vspace{-3mm} 


%Design team
\begin{paracol}{2}
	\textbf{Design Team: EpiX}\\
	\textit{Engineering Lead $\cdot$ Center for Bioengineering Innovation and Design}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Nov 2018 $\sim$ May 2021}
\end{paracol}
%\textit{Advisors: Dr. Youseph Yazdi $\cdot$ Center for Bioengineering Innovation and
%Design (\textbf{CBID}); Martin Jacobsen $\cdot$ Becton Dickson (\textbf{BD})}
\vspace{-5mm}
\begin{itemize}
	\item Perform product research and design novel \textbf{extendable Tuohy needle} 
	prototypes aimed to reduce patient and 
	physician discomfort in current epidural procedures and to save \$162 million/year for 
	hospitals.\vspace{-3mm}
	\item Prototype with Fusion360 CAD software and perform finite
	element analysis (FEA) to test model's efficacy and usability.\vspace{-3mm}
	%\item Collaborate with the School of Medicine and BD to optimize model for clinical and industrial settings.\vspace{-3mm}
	\item Received Malinow Grant (\$4,000) to fund project over 
	summer of 2019 and to seek IRB approval.\vspace{-3mm}
	\item Presented product solution at American Society of Anesthesiologists' 2020 annual meeting. 
\end{itemize}
\vspace{-3mm} 


%Activities & leadership
{\large \textbf{\textsc{Teaching Experience}}}
\vspace{5pt}
\hrule
% Intermediate
\begin{paracol}{2}
	\textbf{Intermediate Programming}\\
	\textit{Course Assistant}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Present}
\end{paracol}
\vspace{-5mm}
\begin{itemize}
	\item TA for core computer science course in C and C++, chosen from a pool of over a hundred highly competitive candidates.\vspace{-3mm}
	\item Help students in class with coding practices, hold office hours, and grade assignments.
\end{itemize}
\vspace{-3mm}

% Physics II
\begin{paracol}{2}
	\textbf{Electromagnetism}\\
	\textit{Learning Assistant}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Jan 2020 $\sim$ May 2020}
\end{paracol}
\vspace{-5mm}
\begin{itemize}
	\item Aided lecture delivery, taught Friday sections to help students solve additional problems, and held office hours weekly.
	\vspace{-3mm}
	\item Compiled notes on mathematical backgrounds of electromagnetism to consolidate understanding of course materials.
\end{itemize}
\vspace{-3mm}

% Volunteer & leadership
{\large \textbf{\textsc{Leadership}}}
\vspace{5pt}
\hrule

%Small group
\begin{paracol}{2}
	\textbf{First-year Mentoring Group}\\
	\textit{Junior Mentor}
	\switchcolumn
	\raggedleft\textbf{Baltimore, MD}\\
	\raggedleft\textit{Aug 2020 $\sim$ Present}
\end{paracol}
\vspace{-5mm}
\begin{itemize}
	\item Support incoming freshmen through the COVID-19 pandemic and navigating an online college experience.
	\vspace{-3mm}
	\item Collaborate with faculty advisers to organize discussions regarding current issues/advancement in computer science.
\end{itemize}
\vspace{-3mm}

% Honduras
\begin{paracol}{2}
	\textbf{Global Medical Brigades}\\
	\textit{Executive Board Member}
	\switchcolumn
	\raggedleft\textbf{Tegucigalpa, Honduras}\\
	\raggedleft\textit{Jan 2019 $\sim$ May 2020}
\end{paracol}
\vspace{-5mm}
\begin{itemize}
	\item Assisted three Honduran communities in building sanitation and clean water infrastructure.\vspace{-3mm}
	\item Headed donation drives with fellow volunteers to gather over 1,400 sanitation bundles to sponsor future brigades.
\end{itemize}

\end{document}
	
